Contribution Title\thanks{Supported by organization x.}

### 2019-11-09 sections/evaluation.tex
add len comparsion plot

Beside solved instances and PAR-2 score, we additionally measure the average clause length and memory consumption for each instances. For $\MapleIUIPPURE$  and $\MapleIUIMIN$, we also captures the $\IUIP$ learning attempted rate and success rate.

@@

\begin{center}
\begin{tabular}{ | m{3.5cm} | m{2cm}| m{2cm} | m{2cm} | m{2cm} | } 
\hline
Solver & \# solved & PAR-2 & Clause Size & Memory \\ 
\hline
$\MapleBase$ & cell5 & cell6 & cell 7 & cell 8 \\ 
\hline
$\MapleIUIPPURE$ & cell8 & cell9 & cell10 & cell11\\ 
\hline
$\MapleIUIMIN$ & cell8 & cell9 & cell10 & cell11\\ 
\hline
\end{tabular}
\end{center}

>>>>

Beside solved instances and PAR-2 score, we additionally measure the average clause length and clause reduction ratio for each instances. For $\MapleIUIPPURE$  and $\MapleIUIMIN$, we also captures the $\IUIP$ learning attempted rate and success rate.

@@

\begin{center}
\begin{tabular}{ | m{3.5cm} | m{2cm}| m{2cm} | m{2cm} | m{2.5cm} | } 
\hline
Solver & \# solved & PAR-2 & Clause Size & Cl Reduction\% \\ 
\hline
$\MapleBase$ & cell5 & cell6 & 59.3 & 37.53\% \\ 
\hline
$\MapleIUIPPURE$ & 221 & cell9 & cell10 & cell11\\ 
\hline
$\MapleIUIMIN$ & 226 & cell9 & 41.5 & 49.5\%\\ 
\hline
\end{tabular}
\end{center}
